continuous tadalafil (by ArticleAggregator_v05)

### 2023-02-17 ArticleAggregatorCS.qmd
Before import of eb_to_merge.xlsx to CodeSpace

```{r}
#| label: Install packages
install.packages("rvest")
install.packages("dplyr")
install.packages("httr")
install.packages("writexl")
install.packages("easyPubMed")

@@

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT",      "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "peripheral edema measurement"
aa_path <- r"(C:\Users\I0172484\Documents\03 - Scripts\R\WebScrap\ArticleAggregator_data\)"
# setwd(aa_path)
```

>>>>

```{r}
#| label: Install packages
install.packages("rvest")
install.packages("dplyr")
install.packages("httr")
install.packages("readxl")
install.packages("writexl")
install.packages("easyPubMed")

@@

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "continuous tadalafil"
aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/"
setwd(aa_path)
```
